Paper 2, Econ 980x

### 2022-11-28 Paper2.Rmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
#library(tinytex)

@@

@@

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
#library(tinytex)
library(ipumsr)

@@

ddi <- read_ipums_ddi("atus_00005.dat")
data <- read_ipums_micro(ddi)

@@

csv %>%
  summary(earnweek)

@@

change4 <- newcsv1 %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = mean_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

@@

delta4 <- change4 %>%
  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
summary(delta4)

delta3 <- change %>%
  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
summary(delta3)

@@

stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "text")
